Hadoop Image Processing Framework

### 2015-03-15 Paper.tex
More copyedits.

\textbf{Step 1: Input a URL List.} Initially user inputs a file containing url's of images to download. The input list should be a text file with one image url per line. The list can be generated by hand, database or a search. The framework provides a extendable ripper module to extract urls from flickr, google and databases. In addition to the list the user will input the type of image bundle to be generated(e.g. har, sequence or map). According to the input, the urls are divided across the nodes for maximum efficiency and parallelism to download the images. Each node map task will generate few image bundles as per the input type containing all the of the images it downloaded. In the reduce phase, the Reducer will merge these image bundles  into a large image bundle.

\textbf{Step 2: Split URLs across nodes.}
From the input, file containing list of image urls and the type of file to be generated, we equally distribute the task of downloading images across the all the nodes in the cluster. The nodes are efficiently managed so that no memory overflow can occur even for terabytes of image downloaded by a single map task. This allows maximum parallelization for downloading. Image urls are distributed to all nodes equally and different map tasks begin downloading the image set it is responsible for.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{down-map}
	\caption{Individual Map task of Downloader Module}
	\label{fig:down-map}
\end{figure}

\textbf{Step 3: Download image data from URLs.}
For every url retrieved in the map task, a connection is established as per transfer protocal (e.g. ftp, http, https etc.). Once connected, we check the file type and if its a valid image we get an InputStream to the connection. From this InputStream, we generate a new HImage object and add the image to the image bundle. The HImage class holds the image data and helps user to play with image and image header data. HImage class also provides an interoperability between various image data types (e.g. BufferedImage, Mat etc.,).

\textbf{ Step 4: Store images in an image bundle. } 
Once HImage object is received, we can add the image to the image bundle simply by passing the HImage object to the appendImage method. Each map task generates a few or many image bundles depending on the image list. In the reduce phase, all these image bundles are merged into one large bundle.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{down-node}
	\caption{Single Node running the Downloader Module handled by the framework and transparent to user}
	\label{fig:down-node}
\end{figure}

\subsection{Processing image bundle using MapReduce}
Hadoop MapReduce programs handle input and output data very efficiently, but the main problem is representing the image data. For instance, to distribute images across map nodes would require to pass images as string, then decode image into a specified format to access pixel information which is not only inefficient but also inconvenient. To overcome this problem we want to able to represent the images as many different formats to increase flexibility. The framework focuses on bringing familiar data types directly to user.

As distribution is important in MapReduce, we want to process the image in the same machine where the bundle block resides. In general, the user needs to create an InputFormat and Record Reader classes to specify the MapReduce job and distribute the input among nodes. This task is a bit cumbersome. In order to make the framework more easier we took care of the InputFormat and RecordReaders.

Images are distributed as various image data types and users can immediately have access to pixel values. As we attempt to obtain the pixel values we lose the valuable image header data(e.g. jpeg exif data, IHDR\cite{David03} Image Header). The framework, holds the image data in a special HImageHeader data type before converting the image bytes into pixel values. After working on the pixel data, it was made sure that image header is appended to the processed pixels. Even though it adds an storage overhead, image header data is preserved even after processing.

The working of Processor module of the framework is described below:

\textbf{Step 1: Input the Algorithm.} We assume that the user writes an algorithm which extends a Generic Algorithm class. This class is passed as an argument to the processor module. The framework starts a MapReduce Job with the algorithm as an input. The GenericAlgorithm holds an HImage variable, this helps user to write an algorithm on the single image which iterates over the whole image bundle. In addition to the algorithm the user should input the image bundle file that needs to be processed. According to the input the image bundle is divided across nodes as individual map task. Each Map task will process the image as of the algorithm and appends them to the output image bundle. In the reduce phase, the Reducer will merge these image bundles into a large image bundle.

\textbf{Step 2: Split Imagebundle across nodes.} The input image bundle is stored in HDFS as blocks. In order to obtain maximum throughput it was made sure the map task is run in the same the block where it resides, using custom input format and record reader classes. This allows maximum parallelization without a problem of transferring data across nodes. The image bundle now executes different map tasks for the image data it is responsible for.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{pro-map}
	\caption{Individual Map task of Processor}
	\label{fig:pro-map}
\end{figure}

>>>>

\textbf{Step 1: Input a URL List.} Initially users input a file
containing URLs of images to download. The input list should be a text
file with one image URL per line. The list can be generated by hand,
extracted from a database or a provided by a search. The framework
provides a extendable ripper module for extracting URLS from Flickr
and Google image searches and from SQL databases. In addition to the
list the user selects the type of image bundle to be generated
(e.g. HAR, sequence or map).  Our system divides the URLs for download
across the available processing nodes for maximum efficiency and
parallelism.  Each node map task generates several image bundles
appropriate to the selected input type, containing all of the images
it downloaded. In the reduce phase, the Reducer will merge these image
bundles into a large image bundle.

\textbf{Step 2: Split URLs across nodes.}  From the input file
containing the list of image URLs and the type of file to be
generated, we equally distribute the task of downloading images across
the all the nodes in the cluster. The nodes are efficiently managed so
that no memory overflow can occur even for terabytes of images
downloaded in a single map task. This allows maximum downloading
parallelization. Image URLs are distributed among all available
processing nodes, and each map task begins downloading its respective
image set.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{down-map}
	\caption{Individual map task of Downloader Module}
	\label{fig:down-map}
\end{figure}

\textbf{Step 3: Download image data from URLs.}  For every URL
retrieved in the map task, a connection is established according to
the appropriate transfer protocol (e.g. FTP, HTTP, HTTPS, etc.). Once
connected, we check the file type.  Valid images are assigned
InputStreams associated with the connection. From these InputStreams,
we generate new HImage objects and add the images to the image
bundle. The HImage class holds the image data and provides an
interface for the user's manipulation of image and image header
data. The HImage class also provides interoperability between various
image data types (e.g. BufferedImage, Mat, etc.).

\textbf{ Step 4: Store images in an image bundle. }  Once an HImage
object is received, it can be added to the image bundle simply by
passing the HImage object to the appendImage method. Each map task
generates a number of image bundles depending on the image list. In
the reduce phase, all of these image bundles are merged into one large
bundle.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{down-node}
	\caption{Single node running the Downloader Module (handled by
          the framework and transparent to the user)}
	\label{fig:down-node}
\end{figure}

\subsection{Processing image bundle using MapReduce}
Hadoop MapReduce programs handle input and output data very
efficiently, but their native data exchange formats are not convenient
for representing or manipulating image data.  For instance,
distributing images across map nodes require the translation of images
into strings, then later decoding these image strings into specified
formats in order to access pixel information.  This is both
inefficient and inconvenient. To overcome this problem, images should
be represented in as many different formats as possible, increasing
flexibility. The framework focuses on bringing familiar data types
directly to user.

As distribution is important in MapReduce, images should be processed
in the same machine where the bundle block resides. In a generic
MapReduce system, the user is responsible for creating InputFormat and
RecordReader classes to specify the MapReduce job and distribute the
input among nodes. This is a cumbersome and error-prone task; the
Hadoop Image Processing Framework provides such InputFormat and
RecordReaders for the sake of the system's ease of use.

Images are distributed as various image data types and users have
immediate access to pixel values.  If pixel values are naively
extracted from the image byte formats, valuable image header data
(e.g. JPEG EXIF data or IHDR \cite{David03} image headers) is
lost. The framework holds the image data in a special HImageHeader
data type before converting the image bytes into pixel values.  After
processing pixel data, image headers are reattached to the processed
results.  The small amount of storage overhead required for this
functionality is a trade-off worth making for the sake of preserving
image header data after processing.

The functionality of the framework's Processor module is described
below:

\textbf{Step 1: Devise the algorithm.} We assume that the user writes
an algorithm which extends the provided GenericAlgorithm class. This
class is passed as an argument to the processor module. The framework
starts a MapReduce job with the algorithm as an input. The
GenericAlgorithm holds an HImage variable; this allows user to write
an algorithm on a single image data structure, which the framework
then iterates over the entire image bundle. In addition to the
algorithm, the user should provide the image bundle file that needs to
be processed.  Depending on the specifics of the image bundle
organization and contents, the bundle is divided across nodes as
individual map tasks. Each map task will apply the processing
algorithm to each local image and append them in turnto the output
image bundle. In the reduce phase, the Reducer merges these image
bundles into a large image bundle.

\textbf{Step 2: Split image bundle across nodes.} The input image
bundle is stored as blocks in the HDFS.  In order to obtain maximum
throughput, the framework establishes each map task to run in the same
block where it resides, using custom input format and record reader
classes. This allows maximum parallelization without the problem of
transferring data across nodes.  Each image bundle now applies
different map tasks to the image data for which it is responsible.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{pro-map}
	\caption{Individual map task of Processor Module}
	\label{fig:pro-map}
\end{figure}
